NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
Update Revision Letter

@@

>>>>

\RC{... the goals of the study and the theoretical framework it uses switch multiple times as the manuscript progresses. Notably, the different models presented on the same dataset are clearly different (in terms of structure, predictors, and outcome variables) and are not clearly related to each other. So the theoretical focus needs to be improved to increase readability and clarity. Specifically, the different models need to be related to other in a theoretical and empirical manner. Also, the main model in figure 2 did not fit well possibly because it assumed conditional independence between three main DTH, DTL, and DRF factors that are expected to covary even after controlling for NFC.}

\Assignment{JZ}
\WorkInProgress
\TimeConsuming

@@

[address frist sentence] We deleted the reference to Grass et al. because referencing it fully would have exceeded the word limit for the abstract.
